Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-07-31 text/paper/paper1.tex
Kleinere Änderungen an 'Materials'

\paragraph{\as- and \es-sentences and positional controls}

We constructed a set of 15 items for \as- and \es-sentences, respectively,
analogous to the examples in ... and ..

Sentences were introduced by a subject DP, including the quantifiers 
{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
one of these"), as well as the head noun which denoted different icons, 
such as letters or bells. Subjects were followed by an auxiliary, and 
a PP containing {\it einige}, a possessive pronoun, and a noun denoting 
a geometrical object, e.g. a triangle or a square. Each sentence was recorded 
with a stressed and an unstressed version of scalar "some" (see section xx 
below). As described in section ..., three control sentences were created 
for each experimental item, corresponding to the critical positions.

Items were evenly distributed across 5 lists using a Latin square design.

\paragraph{Preference-related controls}
For controlling preferences, 28 ambiguous Late closure sentences and 28 
of their disambiguated counterparts were constructed as described in Section ... 
In these sentences, subject DPs were always denoting icons and were followed
by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two PPs.
The first of these PPs consisted in a coordination of two geometrical 
objects, whereas the second PP denoted an icon again. In contrast to these 
sentences, the first part of the conjunct in the unambiguous sentences,was 
modified by a relative clause.

@@

A phonetically trained female native speaker of German was instructed
to realize two prosodic versions of each target sentence, and four
versions of the target-related fillers. In addition to these
sentences, a set of unrelated fillers and neutral control structures
was also recorded. For these constructions, the speaker was instructed
to realize prosodic contours as neutral and natural as possible.

For all target sentences (\as and \es), the determiner \emph{some} was
produced with a contrastive pitch accent as well as with a neutral
accent, respectively. Contrastive accents in German are realized by an
H*L contour (XYZ)\dn{insert references}, thus employing a generally
falling pattern. A set of 15 experimental items was recorded for each
condition (\emph{accented} vs.~\emph{unaccented}), resulting in a
total number of 60 target sentences.

In contrast to the accent manipulation, target-related fillers
differed with respect to prosodic phrasing. Prosodic phrase boundaries
in German are realized by a rise in F0 as well as by a durational
increase on the final part of the constituent preceding the boundary
(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
  Vaissiere, 1983; Fery, 1993}. Boundaries for these filler sentences
were either realized at the position separating the second \acro{pp}
from the preceding material (\emph{late boundary}, corresponding to a
high-attachment reading) or directly preceding the second conjunct in
the first \acro{pp} (\emph{early boundary}, corresponding to a
low-attachment reading). As the prosodic realization of the targets
involved the comparison between an accented and a neutral variant, we
also included a third version of target-related fillers, in which our
speaker produced the sentences without any pronounced
boundaries. Finally, an additional condition was recorded, using
disambiguated sentences that were prosodically neutral (XYZ)\dn{proper
  reference to explanation above}. For each prosodic variant, a set of
30 items was read, yielding 150 target-related fillers. Together with
30 unrelated fillers and 90 control sentences, a total number of 300
sentences was recorded. The session was recorded in an acoustically
shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).

Before entering the judgment task, experimental items and
target-related fillers were analyzed with respect to their acoustic
properties. As both accented elements as well as prosodic boundaries
were expected to differ with respect to their F0 and/or durational
properties, we calculated durational values as well as difference
values between minimal and maximal F0 for each word. As targets
slightly differed with respect to the total number of words as well as
with respect to certain lexical properties (i.e., \emph{seinen}
vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
the following analysis regions:

@@

For the durational analyses, constituents were automatically labeled
by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
obtained values were manually corrected afterwards. For the targets,
two-factorial \acros{anova} with the factors \acro{Quantifier} (all
vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
carried out. For the target-related fillers, we carried out
one-factorial \acros{anova} with the factor \acro{Prosody} (early
boundary, late boundary, neutral prosody). F0 values were extracted by
means of special Praat scripts
(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
differences between minimal and maximal F0 values for each region or
word were calculated. Again, two-factorial \acros{anova} were carried
out for statistical comparison of the fillers, and one-factorial
\acros{anova} were carried out for target-related structures.

A detailed description of our auditory material is found in
Appendix~\ref{sec:audit-sent-mater}.

In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) different boundary realizations for the target- related fillers.
Whereas accented elements clearly differed from their unac-
cented counterpart by showing an increase in duration and F0 range, prosodic
boundaries for our target-related fillers were realized by pre-final lengthening
(i.e. an increase in F0 and duration at the position preceding the boundary).

>>>>

\paragraph{Target sentences and positional controls}

We constructed a set of 15 items for \as- and \es-sentences, respectively,
analogous to the examples in \ref{ex:as} and \ref{ex:es}. Sentences were
introduced by a subject {\small \acro{DP}}, including the quantifiers 
{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
one of these"), as well as the head noun which denoted different icons, 
such as letters or bells. Subjects were followed by an auxiliary, and 
a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares").
The last word was the main verb {\it verbunden} ("connected"). Each sentence was recorded 
in a stressed and an unstressed version of scalar {\it einige} (see section xx 
below). As described above, three control sentences were created 
for each experimental item, corresponding to the critical positions
in the course of uncovering the accompanying sequences (see below).
The positional controls were recorded with neutral prosody.  Items
were evenly distributed across 5 lists using a Latin square design.

\paragraph{Preference-related control sentences}
For controlling preferences, 28 ambiguous Late closure sentences and 28 
of their disambiguated counterparts were constructed as described  above.
In these sentences, subject {\small \acro{DP}}s were always denoting icons and were followed
by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two {\it mit}-{\small \acro{PP}}s.
The first of these {\small \acro{PP}}s consisted in a coordination of two nouns denoting geometrical 
objects, whereas the second PP denoted icons. In contrast to these 
sentences, the unambiguous sentences contained only one PP with a conjunction the first part of which was 
modified by a relative clause.

@@

A phonetically trained female native speaker of German was instructed
to realize two prosodic versions of each target sentence, and three
versions of the ambiguous preference-related controls. In addition to these
sentences, the unambiguous preference-related controls, the positional controls
and a set of unrelated fillers were also recorded. For these constructions, the speaker was instructed
to realize prosodic contours as neutral and natural as possible.

For all target sentences (\as and \es), the determiner \emph{einige} was
produced with a contrastive pitch accent as well as with a neutral
accent. Contrastive accents in German are realized by an
H*L contour (XYZ)\dn{insert references}, thus employing a generally
falling pattern. A set of 15 experimental items was recorded for each
condition (\as vs. \es, \emph{accented} vs.~\emph{unaccented}), resulting in a
total number of 60 target sentences.

In contrast to the accent manipulation, the ambiguous preference-related controls
differed with respect to prosodic phrasing. Prosodic phrase boundaries
in German are realized by a rise in F0 as well as by a durational
increase on the final part of the constituent preceding the boundary
(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
  Vaissiere, 1983; Fery, 1993}. Boundaries for these control sentences
were either realized at the position separating the second {\small \acro{PP}}
from the preceding material (\emph{late boundary}, corresponding to a
high-attachment reading) or directly preceding the second conjunct in
the first {\small \acro{PP}} (\emph{early boundary}, corresponding to a
low-attachment reading). As the prosodic realization of the targets
involved the comparison between an accented and a neutral variant, we
also included a third version of the ambiguous preference related controls, in which our
speaker produced the sentences without any pronounced
boundaries. For each prosodic variant, a set of
30 items was read, yielding 90 target-related fillers.

Altogether a total number of 300 sentences consisting of 60 target sentences, 90 ambiguous preference-related controls, 30 unambiguous preference-related controls, 90 positional control sentences and 30 unrelated fillers was recorded. The session was recorded in an acoustically
shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).

Before entering the judgment task, experimental items and
preference-related fillers were analyzed with respect to their acoustic
properties. As both accented elements as well as prosodic boundaries
were expected to differ with respect to their F0 and/or durational
properties, we calculated durational values as well as difference
values between minimal and maximal F0 for each word. As targets
slightly differed with respect to the total number of words as well as
with respect to certain lexical properties (i.e., \emph{seinen}
vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
the following analysis regions:

@@

For the durational analyses, constituents were automatically labeled
by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
obtained values were manually corrected afterwards. For the targets,
two-factorial \acros{anova} with the factors \acro{Quantifier} (all
vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
carried out. For the target-related fillers, we carried out
one-factorial \acros{anova} with the factor \acro{Prosody} (early
boundary, late boundary, neutral prosody). F0 values were extracted by
means of special Praat scripts
(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
differences between minimal and maximal F0 values for each region or
word were calculated. Again, two-factorial \acros{anova}s were carried
out for statistical comparison of the target sentences, and one-factorial
\acros{anova}s were carried out for preference-related controls.

The details of these analyses are found in
Appendix~\ref{sec:audit-sent-mater}. In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) the expected boundary realizations for the preference-related controls. Whereas accented elements clearly differed from their unaccented counterpart by showing an increase in duration and F0 range, prosodic boundaries for our target-related fillers were realized by pre-final lengthening
(i.e. an increase in F0 and duration at the position preceding the boundary).
